A novel 1000\,MW double-reheat ultra-supercritical system with turbine-extraction-heated air preheaters and low-temperature economizers

### 2018-04-04 article.tex
无改动
引言部分进行了部分修改，添加了几篇参考文献

\section{Introduction}
\label{sec1:intro}
Coal is still the main fossil fuel resource for the production of electricity globally, according to~\cite{Ouedraogo2013Energy}. 
In China, coal–fired power generation accounts for more than 70\% of the total electricity generation and subsequently contributes almost 50\%, 37\%, 33\%, and 55\% to the SO$_X$, NO$_X$, dust, and CO$_X$ emission volumes, respectively~\cite{Zhang2010Analysis}.
Statistics show that China has been the largest producer and consumer of energy worldwide since 2013~\cite{Petroleum2014BP}. 
In 2016, Chinese coal production fell by 7.9\% and the price of steam coal increased by over 60\%~\cite{Petroleum2017BP}. 
Improving system efficiency and reducing coal consumption remain the primary tasks to be considered in power plant design. Nowadays ultra-supercritical (USC) power plants with large capacities and high parameters are considered to be feasible ways to save energy; as such, their usage has spread rapidly worldwide.
The double-reheat USC unit is a new generation of USC unit that can improve thermal performance when compared with a single reheat unit~\cite{Zhao2017Exergy}. 
According to~\cite{Zhao2017Exergy}, a double-reheat unit with the inlet parameter 30.0\,MPa/600/620/620$^\circ$C improves the heat efficiency by 2.4\%-2.6\% when compared with a commonly used USC unit with the inlet parameter 25.0\,MPa/600/600$^\circ$C.
 The United States built the first double-reheat unit with the main parameter 34.4 MPa/649/566/566$^\circ$C in the 1960s.
 Two 700 MW double-reheat USC units were put into operation in Japan in 1990. 
 The process of building five double-reheat USC units began in China in 2012, and three of these units were put into operation in 2015.
 Over the past few decades, double-reheat USC units have received increasing attention due to their rapid development worldwide.

@@

To reduce the energy loss caused by APH, a novel system is proposed in which air is not heated by flue gas in the conventional air preheater. Rather, eight turbine-extraction-heated air preheaters (EAPH1-EAPH8) are used.
The layout of the optimization system is presented in Fig.~\ref{fig:novel_system}.

@@

To rise AOCs' exergy efficiency and to reduce the superheat degree of extractions entering the heat exchangers,
four additional outer steam coolers (AOC1-AOC4) are installed at the air side outlet of EAPH1.
The air side outlet of EAPH1 is sent to the boiler as secondary air, which has a smaller mass and lower heat capacity compared with the feedwater. 
The secondary air temperature thus can increase remarkably, while the LMTD of AOCs can decrease.
The second through the fifth extractions have very high temperatures and great superheat degrees; they are sent to the AOCs in the order of their temperature levels.
For example, the second extraction has the highest temperature and is applied to heat the air in the first AOC. Then the cooled steam from AOC1 is sent to HRH2 and EAPH2 to heat the water and air, respectively.

>>>>

\section{Introduction}
\label{sec1:intro}

By the end of 2017, China's installed capacity of generating units was 1 billion 780 million kilowatts, of which coal-fired units accounted for more than 50\% of the total installed capacity of the country. 
In China, coal–fired power generation accounts for more than 70\% of the total electricity generation and subsequently contributes almost 50\%, 37\%, 33\%, and 55\% to the SO$_X$, NO$_X$, dust, and CO$_X$ emission volumes, respectively~\cite{Zhang2010Analysis} ~\cite{2018}.
Statistics show that China has been the largest producer and consumer of energy worldwide since 2013~\cite{Petroleum2014BP}. 
In 2016, Chinese coal production fell by 7.9\% and the price of steam coal increased by over 60\%~\cite{2017}. 
Improving system efficiency and reducing coal consumption remain the primary tasks to be considered in power plant design. Nowadays ultra-supercritical (USC) power plants with large capacities and high parameters are considered to be feasible ways to save energy; as such, their usage has spread rapidly worldwide.
The double-reheat USC unit is a new generation of USC unit that can improve thermal performance when compared with a single reheat unit~\cite{Zhao2017Exergy}. 
According to~\cite{Zhao2017Exergy}, a double-reheat unit with the inlet parameter 30.0\,MPa/600/620/620$^\circ$C improves the heat efficiency by 2.4\%-2.6\% when compared with a commonly used USC unit with the inlet parameter 25.0\,MPa/600/600$^\circ$C.
 The United States built the first double-reheat unit with the main parameter 34.4 MPa/649/566/566$^\circ$C in the 1960s.
 Two 700 MW double-reheat USC units were put into operation in Japan in 1990. 
 The process of building five double-reheat USC units began in China in 2012, and three of these units were put into operation in 2015.
 Over the past few decades, double-reheat USC units have received increasing attention due to their rapid development worldwide.

@@

To reduce the energy loss caused by APH, a novel system is proposed in which air is not heated by flue gas in the conventional air preheater. Rather, eight turbine-extraction-heated air preheaters (EAPH1-EAPH8) are used.
The layout of the optimization system is presented in Fig.~\ref{fig:novel_system}.
E1-E10 represent the 1st to 10th extraction of steam turbine.

@@

To rise AOCs' exergy efficiency and to reduce the superheat degree of extractions entering the heat exchangers,
four additional outer steam coolers (AOC1-AOC4) are installed at the air side outlet of EAPH1.
The 2nd to 5th extractions are selected as heating sources of AOCs for thier high superheat degree~\cite{Xu2015Optimum,Wang2016}.
After heating the AOCs, the turbine extractions are sent to corresponding regenerative heaters.

In order to match the extractions temperature and the feedwater temperature, the heating steam of AOC1-AOC4 employ 2nd, 4th, 5th and 3rd extraction respectively.

The air side outlet of EAPH1 is sent to the boiler as secondary air, which has a smaller mass and lower heat capacity compared with the feedwater. 
The secondary air temperature thus can increase remarkably, while the LMTD of AOCs can decrease.
The second through the fifth extractions have very high temperatures and great superheat degrees; they are sent to the AOCs in the order of their temperature levels.
For example, the second extraction has the highest temperature and is applied to heat the air in the first AOC. Then the cooled steam from AOC1 is sent to HRH2 and EAPH2 to heat the water and air, respectively.
